Revenue Maximization for Buyers with Costly Participation

### 2025-02-24 paper/paper.tex
Refine and add itnroduction and conclusion

\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{pgf, tikz}
\usepackage{xspace, units}
\usepackage{typearea}
\allowdisplaybreaks

@@

\begin{abstract}
    Test
\end{abstract}

\begin{section}{Introduction}
 Commonly in mechanism design problems auctions are modeled as free to participate in.
 However, this does not necessarily reflect how in reality mechanism exist.
 For example one might need to invest travel costs to arrive to an auction or incur some cost of opportunity.
 All those costs we refer to as participation costs of an auction.
 As buyers might not be convinced to share those costs publically beforehand, e.g. since it is sensitive information, we are studying the problem of private participation costs.

 Recall the setting of the single item auction.
 There is a set $\mathcal{N}$ of $n$ buyers that have interest in buying an item.
 Each buyer has a private valuation $v_i \in \RR_{\geq 0}$.
 A mechanism is a tuple $\mathcal{M} = (x,p)$ of an allocation function $x: \RR \rightarrow [0,1]^n$ and a payment function $p: \RR \rightarrow \RR^n$.
 A players utility with respect to that mechanism is defined as $u_i^\mathcal{M}(v_i) = v_i x_i(v_i) - p_i(v_i)$.

 To model the private participation costs, each player now additionally has participation costs $c_i \in \RR$ \cite{primary}.
 The mechanism $\mathcal{M}' = (x', p')$ will now respect that participation costs as well.
 An player's utility is now reduced by her participation cost if she participates.

@@

 We will now call a player's type the tuple of valuation and participation cost $t_i = (v_i, c_i)$.
 We study the setting where each player's type is drawn from a distribution $\bar{F_i}$.
\end{section}

\begin{section}{Single Buyer Mechanism Design}

 \subsection{Incentive Compatible Mechanism \& Revenue}
 In auction design one usually tries to find incentive compatible mechanism and then to maximize the revenue under the assumptions that players reveal their type truthfully.

 For the first part, in usually single parameter mechanisms \cite{myerson} found a clear characterization of a truthful mechanism.

 \begin{lemma}[\cite{myerson}]
     For single parameter environments, an allocation rule $x$ is implementable if and only if it is monotone.
     If $x$ is monotone, then there exists a unique payment rule $p$, s.t. the mechanism $M=(x,p)$ is truthful
     and $p$ is given by:
     \begin{align*}
         p(v) = v x(v) - \int_0^v x(t) dt + p_0
     \end{align*}
 \end{lemma}

 Also, \cite{primary} came up with a characterization of mechanism which are enough to focus on.

 \begin{lemma}{\cite{primary}}
     \label{lemma:thruthful-mechanism}
     It is without loss for seller to commit to a truthful single parameter mechanism $\mathcal{M}=(x,p)$ and
     for the buyer to participate and truthfully reveal v if and only if $u^\mathcal{M}(v) = \int_0^v x(z)dz - p_0 \geq c$.
 \end{lemma}

 Next to maximize the mechanism one has to find its characteristics as well.
 In the single parameter setting, \cite{myerson} provided such as well.

 \begin{lemma}[\cite{myerson}, Myerson Revenue]
     \label{lemma:myerson-revenue}

@@

 Following from that we derive an expression for the expected revenue for private participation costs.
 For that we first formulize the mechanism described in \autoref{lemma:thruthful-mechanism}.

 Given a truthful single parameter mechanism $\mathcal{M}=(x,p)$.
 For that, we define $v_x(c)$ as the minimum value a player must have, s.t. she would still participate in the mechanism $\mathcal{M}$ when having participation cost $c$.

 \begin{align*}
     v_x(c) = \inf_{v \in \RR_{\geq 0}} \{vx(v) - p(v) \geq c\}
 \end{align*}

 Next we can define the allocation function $x_c$ as simply implementing the characterization of \autoref{lemma:thruthful-mechanism},
 by allocating $x(v)$ if the player has a value that is at least $v_x(c)$ and $0$ otherwise.

 \begin{align*}
     x_c(v) = \begin{cases}
                  x(v) & v \geq v_x(c)    \\
                  0    & \text{otherwise}
              \end{cases}
 \end{align*}

 Similar the payment rule $p_c(v)$ delegates the payment rule $p$ in the case that $v \geq v_x(c)$ and otherwise expects no payment.
 Together, they define the mechanism $\mathcal{M}_c = (x_c, p_c)$ induced by the mechanism $\mathcal{M}$.

 If we now define a virtual value function that is conditional on $c$, by using the conditional cumulative distribution $\bar{F}_c$ and the conditional density function $\hat{f}_c$ as
 $\varphi_c(v) = v - (1- \bar{F}_c(v)) / \hat{f}_c(v)$ then we can express the expected revenue in \autoref{theorem:expected-revenue}.

 \begin{theorem}[\cite{primary}]
     \label{theorem:expected-revenue}
     Given any $\bar{F}$ with marginal cost distribution $G$, any mechanism $\mathcal{M}=(x,p)$, then the expected revenue $\mathbf{E}_{t \sim \bar{F}}\left[p_c(v)\right]$ of the seller is

@@

 \begin{proof}
     We proof this using a case distinction and then draw the expectation.
     First start by fixing $c$ arbitrarily.
     Consider the case that $c > -p_0$. Note that $-p_0$ corresponds to a payment the player would get from the mechanism for participating.
     That means in the case that $c > -p_0$, we do not simply always participate, since our utility could be negative. Therefore, we also have $v_x(c) > 0$.

     We first consider the case that we participate, i.e. $v \geq v_x(c)$.
     In that case the payment the player has to pay the payment $p(v)$ of the single parameter mechanism.

     \begin{align}
         \label{eq:payment-participating}
         p_c(v) = p(v) = v x(v) - \int_0^v x(t) dt + p_0
     \end{align}

     We use linearity of the integral and the definition of utility to express this in terms of the allocation function $x_c$.
     \begin{align*}
         \int_0^v x(t) dt & = \int_0^{v_c(x)} x(t) dt + \int_{v_c(x)}^v x(t) dt     \\
                          & = u^\mathcal{M}(v_c(x)) + p_0 + \int_{v_c(x)}^v x(t) dt \\
                          & = c + p_0 + \int_{v_c(x)}^v x(t) dt
     \end{align*}
     Here the last step uses that $u^\mathcal{M}(v_c(x)) = c$ per definition of $v_c(x)$.

     Plugging this into \autoref{eq:payment-participating} yields
     \begin{align*}
         p_c(v) = v x_c(v) - \int_0^v x_c(t) dt - c
     \end{align*}

     Next we consider the case that the player does not participate, i.e. $v < v_x(c)$.
     In that case, the payment rule requests no payment, i.e. $p_c(v) = 0$, yet conveniently some part of the expression found before are also $0$:

     \begin{align*}
         p_c(v) = 0 = v x_c(v) - \int_0^v x_c(t) dt
     \end{align*}

     Thus, we can represent this entire case using an indicator function:
     \begin{align*}
         p_c(v) = 0 = v x_c(v) - \int_0^v x_c(t) dt - c \1{v \geq v_x(c)}
     \end{align*}

     Drawing the expectation around the value $v \sim \bar{F}_c$ while keeping the participation cost still fixed yields

     \begin{align*}
         \Ex[v \sim \bar{F}_c]{p_c(v)} & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t) dt - c \1{v \geq v_x(c)}}   \\
                                       & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t) dt} - \Pr{v \geq v_x(c)}c   \\
                                       & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} - (1 - \bar{F}_c(v_x(c))) \cdot c \\
     \end{align*}

     Here in the last step we used that for fixed $c$, $M_c$ is a truthful mechanism thus we can apply \autoref{lemma:myerson-revenue}, and we also used the cumulative distribution.

     Now we consider the opposite case, that is that $c \leq -p_0$.
     Analogously to the case before, $c \leq -p_0$ means that the mechanism's payment for simply participating already pays of our participation cost.
     Certainly in that case $v_x(c) = 0$.

     Therefore, the player always participates and pays $p(v)$. In the case that $v_x(c) = 0$, we have $x_c(v) = x(v)$ for all $v \in \RR_{\geq 0}$, therefore:
     \begin{align*}
         p_c(v) = p(v) = v x(v) - \int_0^v x(t)dt + p_0 = v x_c(v) - \int_0^v x_c(t)dt + p_0
     \end{align*}

     Drawing again the expectation around the value $v \sim \bar{F}_c$ while keeping the participation cost still fixed yields

     \begin{align*}
         \Ex[v \sim \bar{F}_c]{p_c(v)} & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t)dt + p_0}                  \\
                                       & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + p_0                           \\
                                       & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + (1 - \bar{F}_{c}(v_x(c))) p_0
     \end{align*}

     Where in the last equality, we used that since $v_x(c) = 0$, $\bar{F}_{c}(v_x(c)) = 0$ as well.

     Now we can finally draw the expectation around the previously fixed $c$ and get to the wished theorem:

@@

 \subsection{Revenue Maximization}

 We observe that this problem is inherently non-convex. Even more, \cite{primary} showed that it is not even reparameterizedable as a convex problem.
 Due to that we cannot hope to calculate revenue optimal mechanisms in general in polynomial time.

 Therefore, \cite{primary} propose to introduce a fully polynomial-time approximation scheme (FPTAS).

 First we will normalize $v$ to $[0,1]$.
 Next, let $\epsilon \in (0, 1)$ be the approximation degree.
 Let $\bar{F}'$ be the value distribution with the value rounded down to the nearest multiple of $\epsilon$.
 Since still there are infinitely many allocation functions, we discretize those two by only allocating multiples of $\epsilon$ as well.

 This leads us to a problem definition for which an optimal mechanism is computable in polynomial time w.r.t. to $\frac{1}{\epsilon}$.
 We will see later how to do this.
 Still it is not clear that this mechanism is close to the optimal mechanism for the original problem.

@@

 To proof this we make use of the following lemmas without proofs:
 \begin{lemma}[\citet{primary}]
     \label{lemma:allocation-function-within-e}
     For any distribution $\bar{F}$ supported on $[0,1]^2$ and for any pair of mechanisms $\mathcal{M}'$ and $\widehat{\mathcal{M}}$
     with allocation rules $x'$ and $\hat{x}$, s.t. $x'(v) \in [\hat{x}(v), \hat{x}(v) + \epsilon]$ for all $\epsilon$, we have $\mathrm{Rev}(\bar{F}, \mathcal{M}') \geq \mathrm{Rev}(\bar{F}, \widehat{\mathcal{M}}) - \epsilon$.
 \end{lemma}
 \begin{lemma}[\citet{primary}]
     \label{lemma:difference-in-optimal-mechanims}
     Let $(\Omega, \mathcal{F}, P)$ be any probability measure and let $t_1, t_2: \Omega \rightarrow \mathbb{R}^2$ be two 2-dimensional random variables.
     If $\sup_{\omega \in \Omega} || t_1(\omega) - t_2(\omega) ||_\infty \leq \epsilon$, then $|\mathrm{OPT}(t_1) - \mathrm{OPT}(t_2)| \leq 3\epsilon$.
 \end{lemma}

@@

     Next, we define $\widehat{\mathcal{M}}$ as the optimal mechanism on $\bar{F}'$ (one that is allowed to allocate continuous values).
     Next, we make use of \autoref{lemma:allocation-function-within-e}, since our allocation function $x'$ of mechanism $\mathcal{M}'$
     allocates within an $\epsilon$-interval of the allocation function $\hat{x}$ of $\widehat{\mathcal{M}}$.
     Thus, according to \autoref{lemma:allocation-function-within-e}, we got $\mathrm{Rev}(\bar{F}', \mathcal{M}') \geq \mathrm{Rev}(\bar{F}', \widehat{\mathcal{M}}) - \epsilon$.

     Finally, note, that for the two type distributions $\bar{F}$ and $\bar{F}'$ it holds that they originate from the same probability measure, yet the value of the random variables differs by at most $\epsilon$.
     Also note, that we did not round the participation cost, thus the difference with respect to the infinity-norm $|| \cdot ||_{\infty}$ is also at most $\epsilon$.
     Therefore, we can apply \autoref{lemma:difference-in-optimal-mechanims}, since $\widehat{\mathcal{M}}$ is optimal mechanism on $\bar{F}'$,
     we get $\mathrm{Rev}(\bar{F}', \widetilde{\mathcal{M}}) \geq \mathrm{OPT}(\bar{F}') - 3\epsilon$.

     If we put now all together, we get:
     \begin{align*}
         \mathrm{Rev}(\bar{F}, \mathcal{M}') & \geq \mathrm{Rev}(\bar{F}', \mathcal{M}')                     \\
                                             & \geq \mathrm{Rev}(\bar{F}', \widehat{\mathcal{M}}) - \epsilon \\
                                             & \geq \mathrm{OPT}(\bar{F}') - 4\epsilon
     \end{align*}
 \end{proof}

 Now that we know that the difference in the problem statement leads to an reasonable approximation guarantee,
 we can now dedicate to finding an optimal mechanism for this problem.

 We will use a dynamic program based on the approximation degree $\epsilon$ to calculate for all possible valuations
 an allocation function that optimizes the revenue.
 We will make sure this allocation rule is non-decreasing and will follow the payment rule through \autoref{lemma:thruthful-mechanism}
 in order to also get a truthful mechanism.

 For $i,j \leq \frac{1}{\epsilon}$ and $k \leq \frac{1}{\epsilon^2}$,
 we define $R(i,j,k)$ as the optimal revenue from only a subset of the buyers, i.e. those that have a value $v \leq i \epsilon$
 and for which the allocation function is fixed to $x(i \epsilon) = j \epsilon$ and the utility is also fixed to $u(i \epsilon) = k \epsilon^2$.
 Observe that in this formulation, we can express it in terms of an expectation:

@@

 \begin{theorem}
     \label{theorem:recursion-formular}
     For $i \geq 2$ $R(i,j,k)$ can be calculated as follows:

     \begin{align*}
         R(i,j,k) = \max_{j' \leq j} R(i-1, j, k - j) + q_i \bar{F}_i'(k \epsilon^2) \cdot (i\cdot j - k)\epsilon^2
     \end{align*}

     where $q_i$ refers to the occurrence probability of $v = i \epsilon$ and $\bar{F}_i'$ refers to the cumulative type distribution conditional on the value being $i\epsilon$.
 \end{theorem}

>>>>

\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{thmtools}
\usepackage{hyperref}
\usepackage{pgf, tikz}
\usepackage{xspace, units}
\usepackage{typearea}
\allowdisplaybreaks

@@

\begin{abstract}
    In mechanism design, usually expected revenue optimal mechanism given the distributions of buyers' values are searched.
    However practically this is not the only information of buyers that matters for buyer decisions.
    Participation costs are one attribute which is practically relevant, yet revenue optimal mechanisms for private participation costs are unknown.
    We study exactly this mechanism design problem.
    We derive a formulation of the expected revenue in the model that takes private participation costs into account, however realize that it is a non-convex problem.
    Therefore, we find a fully polynomial approximation scheme (FPTAS) for single buyer that computes a $\mathrm{OPT} - 4\epsilon$ approximation of the optimal revenue in $\mathrm{poly}\left(\frac{1}{\epsilon}\right)$ running time.
\end{abstract}

\begin{section}{Introduction}
 Commonly in mechanism design problems auctions are modeled as free to participate in.
 However, this does not necessarily reflect how in reality mechanism exist.
 For example, consider the case that for moving to a new city one wants to buy a house that is sold in an auction.
 To participate there one at least need to be present and therefore might pay for travel, accommodation and also incur some loss opportunity for not being at the regular workplace.
 All those costs we refer to as participation costs of an auction for this buyer.
 As buyers might not be convinced to share those costs publically beforehand, e.g. since it might be sensitive information, we are studying the problem of private participation costs.

 We study this mechanism design problem.
 Based on the work of \citet{primary}, we derive a model in \autoref{sec:model} that incorporates private participation costs as well as valuations.
 Next we focus on finding a formulation of the expected revenue that is to be maximized as also done by \citet{myerson} in \autoref{sec:incentive-comptaible-mechanism-revenue}.
 We will see that this problem because inherently non-convex and thus we focus on finding an FPTAS that achieves a $\mathrm{OPT} - 4\epsilon$ approximation of the optimum single buyer mechanism in \autoref{sec:revenue-maximization}.
\end{section}

\begin{section}{Model}
 \label{sec:model}
 Recall the setting of the single item auction.
 There is a set $\mathcal{N}$ of $n$ buyers that have interest in buying an item.
 Each buyer has a private valuation $v_i \in \RR_{\geq 0}$.
 A mechanism is a tuple $\mathcal{M} = (x,p)$ of an allocation function $x: \RR \rightarrow [0,1]^n$ and a payment function $p: \RR \rightarrow \RR^n$.
 A buyer's utility with respect to that mechanism is defined as $u_i^\mathcal{M}(v_i) = v_i x_i(v_i) - p_i(v_i)$.

 To model the private participation costs, each buyer now additionally has participation costs $c_i \in \RR$ \cite{primary}.
 The mechanism $\mathcal{M}' = (x', p')$ will now respect that participation costs as well.
 An buyer's utility is now reduced by her participation cost if she participates.

@@

 We will now call a buyer's type the tuple of valuation and participation cost $t_i = (v_i, c_i)$.
 We study the setting where each buyer's type is drawn from a distribution $\bar{F_i}$.
\end{section}

\begin{section}{Single Buyer Mechanism Design}
 In this work, the entire focus lies on the case where there exists only a single buyer.
 Thus, the subscript $i$ in our notation will be dropped.
 Later we will give an outlook on how \citet{primary} employ a reduction from the many-buyer mechanism design problem to the single buyer one.
 This reduction framework was first introduced by \citet{alaei2012bayesian,alaei2014bayesian}.

 \subsection{Incentive Compatible Mechanism \& Revenue}
 \label{sec:incentive-comptaible-mechanism-revenue}
 In auction design one usually tries to find incentive compatible mechanism and then to maximize the revenue under the assumptions that buyers reveal their type truthfully.

 For the first part, in usually single parameter mechanisms \citet{myerson} found a clear characterization of a truthful mechanism (\autoref{lemma:myersons-lemma}).

 \begin{lemma}[Myerson's Lemma \cite{myerson}]
     \label{lemma:myersons-lemma}
     For single parameter environments, an allocation rule $x$ is implementable if and only if it is monotone.
     If $x$ is monotone, then there exists a unique payment rule $p$, s.t. the mechanism $\mathcal{M}=(x,p)$ is truthful
     and $p$ is given by:
     \begin{align*}
         p(v) = v x(v) - \int_0^v x(t) dt + p_0
     \end{align*}
 \end{lemma}

 Also, \citet{primary} found that we can base our work on Myerson's Lemma (\ref{lemma:myersons-lemma})
 by generalizing a truthful single-parameter mechanism to a one that takes participation cost into account (\autoref{lemma:thruthful-mechanism}).

 \begin{lemma}[Incentive Compatibile Mechanism \cite{primary}]
     \label{lemma:thruthful-mechanism}
     It is without loss for seller to commit to a truthful single parameter mechanism $\mathcal{M}=(x,p)$ and
     for the buyer to participate and truthfully reveal v if and only if $u^\mathcal{M}(v) = \int_0^v x(z)dz - p_0 \geq c$.
 \end{lemma}

 Next to maximize the mechanism one has to find its characteristics as well.
 In the single parameter setting, again \citet{myerson} provided such as well (\autoref{lemma:myerson-revenue}).

 \begin{lemma}[Myerson's Revenue \cite{myerson}]
     \label{lemma:myerson-revenue}

@@

 Following from that we derive an expression for the expected revenue given private participation costs.
 For that we first formulize the mechanism described in \autoref{lemma:thruthful-mechanism}.

 Given a truthful single parameter mechanism $\mathcal{M}=(x,p)$.
 For that, we define $v_x(c)$ as the minimum value a buyer must have, s.t. she would still participate in the mechanism $\mathcal{M}$ when having participation cost $c$.

 \begin{align*}
     v_x(c) = \inf_{v \in \RR_{\geq 0}} \{\underbrace{vx(v) - p(v) \geq c}_{u^\mathcal{M}(v)}\}
 \end{align*}
 Next we can define the allocation function $x_c$ as simply implementing the characterization of \autoref{lemma:thruthful-mechanism},
 by allocating $x(v)$ if the buyer has a value that is at least $v_x(c)$ and $0$ otherwise.

 \begin{align*}
     x_c(v) = \begin{cases}
                  x(v) & v \geq v_x(c)    \\
                  0    & \text{otherwise}
              \end{cases}
 \end{align*}
 Similar the payment rule $p_c(v)$ delegates the payment rule $p$ in the case that $v \geq v_x(c)$ and otherwise expects no payment.
 Together, they define the mechanism $\mathcal{M}_c = (x_c, p_c)$ induced by the mechanism $\mathcal{M}$.
 See \autoref{fig:visualization-of-induced-mechanism} for a visualization of the allocation rule.

 \begin{figure}[htp!]
     \centering

     \begin{subfigure}{.4\textwidth}
         \centering
         \begin{tikzpicture}
             \draw (0,0) -- (2.5,0) node[right] {\( c \)};
             \draw (0,0) -- (0,2.5) node[above] {\( v_x(c) \)};

             \draw[thick,domain=0:2] plot (\x,{0.5+\x});
         \end{tikzpicture}
         \caption{
             $\mathbf{v_x(c)}$: Minimum value $v$, s.t. the utility with respect to the single parameter mechanism is at least the participation cost.
         }
     \end{subfigure}
     \begin{subfigure}{.4\textwidth}
         \centering
         \begin{tikzpicture}
             \draw (0,0) -- (2.5,0) node[right] {$v$};
             \draw (0,0) -- (0,2.5) node[above] {$x_c(v)$};

             \draw[dashed, gray] (0,0) -- (1,0);
             \draw[dashed, gray] (1,2) -- (2.5,2);
             \draw[dashed, gray] (1,0) -- (1,2);

             \draw[thick] (0,0) -- (1.5,0);
             \draw[thick] (1.5,2) -- (2.5,2);
             \draw[thick] (1.5,0) -- (1.5,2);
             \node[above] at (1.5,2) {$v_x(c)$};

             \node[left] at (0,2) {$1$};
             \node[left, gray] at (1,2) {$x(v)$};
         \end{tikzpicture}
         \caption{
             $\mathbf{\mathbf{x_c(v)}}$: Allocates the item using single parameter allocation rule $x(v)$ if the value is at least minimal value to particpate with $v_x(c)$.
         }
     \end{subfigure}
     \caption{
         Exemplary visualization of $v_x(c)$ and the induced allocation rule $x_c(v)$.
     }
     \label{fig:visualization-of-induced-mechanism}
 \end{figure}

 If we now define a virtual value function that is conditional on $c$, by using the conditional cumulative distribution $\bar{F}_c$ and the conditional density function $\hat{f}_c$ as
 $\varphi_c(v) = v - \frac{1- \bar{F}_c(v)}{\hat{f}_c(v)}$ then we can express the expected revenue in \autoref{theorem:expected-revenue}.

 \begin{theorem}[Expected Revenue \cite{primary}]
     \label{theorem:expected-revenue}
     Given any $\bar{F}$ with marginal cost distribution $G$, any mechanism $\mathcal{M}=(x,p)$, then the expected revenue $\Ex[t \sim \bar{F}]{p_c(v)}$ of the seller is

@@

 \begin{proof}
     We proof this using a case distinction and then draw the expectation.
     First start by fixing $c$ arbitrarily.

     Consider the case that $c > -p_0$. Note that $-p_0$ corresponds to a payment the buyer would get from the mechanism for participating.
     That means in the case that $c > -p_0$, we do not simply always participate, since our utility could be negative. Therefore, we also have $v_x(c) > 0$.
     We first consider the case that we participate, i.e. $v \geq v_x(c)$.
     In that case the buyer has to pay $p(v)$.
     \begin{align}
         \label{eq:payment-participating}
         p_c(v) = p(v) = v x(v) - \int_0^v x(t) dt + p_0
     \end{align}
     We use linearity of the integral and the definition of utility to express this in terms of the allocation function $x_c$.
     \begin{equation}
         \label{eq:utility-participating}
         \begin{aligned}
             \int_0^v x(t) dt & = \int_0^{v_c(x)} x(t) dt + \int_{v_c(x)}^v x(t) dt     \\
                              & = u^\mathcal{M}(v_c(x)) + p_0 + \int_{v_c(x)}^v x(t) dt \\
                              & = c + p_0 + \int_{v_c(x)}^v x(t) dt
         \end{aligned}
     \end{equation}
     Here the last step uses that $u^\mathcal{M}(v_c(x)) = c$ per definition of $v_c(x)$.
     Plugging \autoref{eq:utility-participating} into \autoref{eq:payment-participating} yields \autoref{eq:payment-participating-final}:
     \begin{align}
         \label{eq:payment-participating-final}
         p_c(v) = v x_c(v) - \int_0^v x_c(t) dt - c
     \end{align}
     Next we consider the case that the buyer does not participate, i.e. $v < v_x(c)$.
     In that case, the payment rule requests no payment, i.e. $p_c(v) = 0$, yet conveniently some part of the expression found before are also $0$:
     \begin{align*}
         p_c(v) = 0 = v x_c(v) - \int_0^v x_c(t) dt
     \end{align*}
     Thus, we can represent this entire case using an indicator function:
     \begin{align*}
         p_c(v) = 0 = v x_c(v) - \int_0^v x_c(t) dt - c \1{v \geq v_x(c)}
     \end{align*}
     Drawing the expectation around the value $v \sim \bar{F}_c$ while keeping the participation cost still fixed yields
     \begin{equation}
         \label{eq:expected-revenue-first-case}
         \begin{aligned}
             \Ex[v \sim \bar{F}_c]{p_c(v)} & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t) dt - c \1{v \geq v_x(c)}}   \\
                                           & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t) dt} - \Pr{v \geq v_x(c)}c   \\
                                           & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} - (1 - \bar{F}_c(v_x(c))) \cdot c \\
         \end{aligned}
     \end{equation}
     Here in the last step we used that for fixed $c$, $M_c$ is a truthful mechanism thus we can apply \autoref{lemma:myerson-revenue}, simultaneously we use the definition of the cumulative distribution.

     Now we consider the opposite case, that is that $c \leq -p_0$.
     Analogously to the case before, $c \leq -p_0$ means that the mechanism's payment for simply participating already pays of our participation cost.
     Certainly in that case $v_x(c) = 0$.
     Therefore, the buyer always participates and pays $p(v)$. In the case that $v_x(c) = 0$, we have $x_c(v) = x(v)$ for all $v \in \RR_{\geq 0}$, therefore:
     \begin{align*}
         p_c(v) = p(v) = v x(v) - \int_0^v x(t)dt + p_0 = v x_c(v) - \int_0^v x_c(t)dt + p_0
     \end{align*}
     Drawing again the expectation around the value $v \sim \bar{F}_c$ while keeping the participation cost still fixed yields
     \begin{equation}
         \label{eq:expected-revenue-second-case}
         \begin{aligned}
             \Ex[v \sim \bar{F}_c]{p_c(v)} & = \Ex[v \sim \bar{F}_c]{v x_c(v) - \int_0^v x_c(t)dt + p_0}                  \\
                                           & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + p_0                           \\
                                           & = \Ex[v \sim \bar{F}_c]{x_c(v) \varphi_c(v)} + (1 - \bar{F}_{c}(v_x(c))) p_0
         \end{aligned}
     \end{equation}
     Where in the last equality, we used that since $v_x(c) = 0$, $\bar{F}_{c}(v_x(c)) = 0$ as well.

     Now we can finally draw the expectation around the previously fixed $c$, combine \autoref{eq:expected-revenue-first-case} and \autoref{eq:expected-revenue-second-case} to get the wished theorem:

@@

 Since we focus on revenue maximization, it is w.l.o.g. to consider $p_0 \geq 0$.
 Further \citet{primary} showed that for any mechanism with $p_0 \geq 0$ there exists a mechanism with weakly higher revenue with $p_0 = 0$.
 Therefore, from now on, we disregard $p_0$.

 \subsection{Revenue Maximization}
 \label{sec:revenue-maximization}

 We observe that this problem is inherently non-convex.
 Even more, \citet{primary} showed that for multiple buyer it is not even representable as a convex program in general.
 Due to that, we cannot hope to calculate revenue optimal mechanisms in general in polynomial time.
 Therefore, \citet{primary} propose to introduce a fully polynomial-time approximation scheme (FPTAS).

 First we focus on type distributions $\bar{F}$ where $v$ is normalized to $[0,1]$.
 Next, let $\epsilon \in (0, 1)$ be the approximation degree.
 Let $\bar{F}'$ be the value distribution with the value rounded down to the nearest multiple of $\epsilon$.
 Since there are still infinitely many allocation functions, we discretize those as well by only allocating multiples of $\epsilon$.

 This leads us to a problem definition for which an optimal mechanism is computable in polynomial time with respect to $\frac{1}{\epsilon}$.
 We will see later how to do this.
 Still it is not clear that this mechanism is close to the optimal mechanism for the original problem.

@@

 To proof this theorem we make use of the following lemmas without proofs:

 \begin{lemma}[\citet{primary}]
     \label{lemma:allocation-function-within-e}
     For any distribution $\bar{F}$ supported on $[0,1]^2$ and for any pair of mechanisms $\mathcal{M}'$ and $\widehat{\mathcal{M}}$
     with allocation rules $x'$ and $\hat{x}$, s.t. $x'(v) \in [\hat{x}(v), \hat{x}(v) + \epsilon]$ for all $\epsilon$, we have $\mathrm{Rev}(\bar{F}, \mathcal{M}') \geq \mathrm{Rev}(\bar{F}, \widehat{\mathcal{M}}) - \epsilon$.
 \end{lemma}
 \begin{lemma}[\citet{primary}]
     \label{lemma:difference-in-optimal-mechanisms}
     Let $(\Omega, \mathcal{F}, P)$ be any probability measure and let $t_1, t_2: \Omega \rightarrow \mathbb{R}^2$ be two 2-dimensional random variables.
     If $\sup_{\omega \in \Omega} || t_1(\omega) - t_2(\omega) ||_\infty \leq \epsilon$, then $|\mathrm{OPT}(t_1) - \mathrm{OPT}(t_2)| \leq 3\epsilon$.
 \end{lemma}

@@

     Next, we define $\widehat{\mathcal{M}}$ as the optimal mechanism on $\bar{F}'$ (one that is allowed to allocate continuous values).
     We use \autoref{lemma:allocation-function-within-e}, since our allocation function $x'$ of mechanism $\mathcal{M}'$
     allocates within an $\epsilon$-interval of the allocation function $\hat{x}$ of $\widehat{\mathcal{M}}$.
     Thus, according to \autoref{lemma:allocation-function-within-e}, we got $\mathrm{Rev}(\bar{F}', \mathcal{M}') \geq \mathrm{Rev}(\bar{F}', \widehat{\mathcal{M}}) - \epsilon$.

     Finally, note, that for the two type distributions $\bar{F}$ and $\bar{F}'$ it holds that they originate from the same probability measure, yet the value of the random variables differs by at most $\epsilon$.
     Also note, that we did not round the participation cost, thus the difference with respect to the infinity-norm $|| \cdot ||_{\infty}$ is also at most $\epsilon$.
     Therefore, we can apply \autoref{lemma:difference-in-optimal-mechanisms}, since $\widehat{\mathcal{M}}$ is optimal mechanism on $\bar{F}'$,
     to get $\mathrm{Rev}(\bar{F}', \widehat{\mathcal{M}}) \geq \mathrm{OPT}(\bar{F}') - 3\epsilon$.

     Putting everything together yields the stated approximation guarantee:
     \begin{align*}
         \mathrm{Rev}(\bar{F}, \mathcal{M}') & \geq \mathrm{Rev}(\bar{F}', \mathcal{M}')                     \\
                                             & \geq \mathrm{Rev}(\bar{F}', \widehat{\mathcal{M}}) - \epsilon \\
                                             & \geq \mathrm{OPT}(\bar{F}') - 4\epsilon
     \end{align*}
 \end{proof}

 Now that we know that the difference in the problem statement leads to a reasonable approximation guarantee,
 we can dedicate ourselves to finding an optimal mechanism for this problem.

 We will use a dynamic program based on the approximation degree $\epsilon$ to calculate for all possible valuations
 an allocation function that optimizes the revenue.
 We will make sure this allocation rule is non-decreasing and will follow the payment rule through \autoref{lemma:thruthful-mechanism}
 in order to also get a truthful mechanism.
 Note that \autoref{lemma:thruthful-mechanism} also tells us, that it is enough to find a single parameter allocation rule and optimize the revenue of the induced mechanism $\mathcal{M}_c$ with payment rule $p_c$.

 For $i,j \leq \frac{1}{\epsilon}$ and $k \leq \frac{1}{\epsilon^2}$,
 we define $R(i,j,k)$ as the optimal revenue from only a subset of the buyers, those that have a value $v \leq i \epsilon$
 and while the allocation function is fixed for $i\epsilon$ to $x(i \epsilon) = j \epsilon$ and the utility is also fixed to $u(i \epsilon) = k \epsilon^2$.
 Observe that in this formulation, we can express it in terms of an expectation:

@@

 \begin{theorem}
     \label{theorem:recursion-formular}
     For $i \geq 2$, $R(i,j,k)$ can be calculated as follows:
     \begin{align*}
         R(i,j,k) = \max_{j' \leq j} R(i-1, j, k - j) + q_i \bar{F}_i'(k \epsilon^2) \cdot (i\cdot j - k)\epsilon^2
     \end{align*}
     where $q_i$ refers to the occurrence probability of $v = i \epsilon$ and $\bar{F}_i'$ refers to the cumulative type distribution conditional on the value being $i\epsilon$.
 \end{theorem}

 See \autoref{fig:fptas-recursion-formular} for a visualization of this theorem.

 \begin{figure}[htp!]
     \centering
     \begin{tikzpicture}[
             node/.style={circle, draw=black, fill=gray!20, scale=.3},
             axis/.style={->, thick},
             gridline/.style={gray, dashed}
         ]

         \draw[axis] (0, 0) -- (4.5, 0) node[right] {$i$};
         \draw[axis] (0, 0) -- (0, 4.5) node[above] {$j$};

         \foreach \x in {1, 2, 3, 4} {
                 \draw[gridline] (\x, 0) -- (\x, 4.5);
                 \draw[gridline] (0, \x) -- (4.5, \x);
             }

         \foreach \i in {1, 2, 3, 4} {
                 \foreach \j in {1, 2, 3, 4} {
                         \ifthenelse{\i=3\and\j=2}
                         {
                             \node[node, fill=green!20] at (\i, \j) {$R(\i,\j,k -2)$};
                         }
                         {
                             \ifthenelse{\i=2\and\j<3}
                             {
                                 \node[node, fill=blue!20] at (\i, \j) {$R(\i,\j,k - 2)$};
                             }
                             {
                                 \node[node] at (\i, \j) {$R(\i,\j,k - 2)$};
                             }
                         }
                     }
             }

         \node at (0, 0) [below left] {0};
         \foreach \x in {1, 2, 3, 3, 4} {
                 \node at (0, \x) [left] {\x};
                 \node at (\x, 0) [below] {\x};
             }
     \end{tikzpicture}
     \caption{
         Visualization of \autoref{theorem:recursion-formular}. For $R(3,2,k)$ we need to maximize over all $R(2, j', k-j)$ where $j' \leq j = 2$.
     }
     \label{fig:fptas-recursion-formular}
 \end{figure}
